A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-06-10 ms.tex
Fixing nits from Monday datacon

@@

\begin{abstract}
We present a catalog of broad-band spectral measurements from the 
Donald C. Backer Precision Array for Probing
the Epoch of Reionization (PAPER) in South Africa observed in July and
September of 2011.  In order to reduce the impact of beam calibration, which proves to
be a difficult endeavor for transit telescopes such as PAPER, on the determination
of source spectra, we have focused on calibrating sources in a narrow declination range.
Since each source follows a nearly identical path through the primary beam, this
restriction allows beam calibration to be greatly reduced as a source of error,
yielding a dramatic improvement in the accuracy of source spectra measured in the 
100--200-MHz band which is receiving renewed attention by experiments seeking to
measure 21cm emission from the Epoch of Reionization (EoR). Using beam forming
and fringe-rate filtering we measure spectra for Pictor A, which provides a key flux reference for PAPER's EoR
power spectrum analysis, 
as well as 60 other sources at nearby declinations. Extrapolating from higher frequency
catalogs we set the flux scale in a monte-carlo fit across multiple sources. This fit 
propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
2.4\%.
This accuracy is limited by the uncertainty in the catalog measurements we use
to estimate an absolute flux scale, and represents 
an order of magnitude improvement over previous measurements in this band.  
Comparing with prior measurements, 45 out
of 58 sources observed are found to confirm and refine a power-law model for flux density.

@@

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{furlanetto_et_al2006}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued
foreground characterization is a
vital step en route to any 21-cm EoR detection.
At these low
frequencies the Southern sky is much less well known than the North, 
with catalog source fluxes at 150MHz being inaccurate at the 20\% level
for $\delta<-20$\arcdeg (XXX cite).
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.

@@

In this paper, we set out to significantly improve the accuracy of spectral measurements between 
100--200 MHz for a set of bright sources in the declination range XXX to XXX that
are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
Using the fact that, for this restricted declination range,
sources transit through a nearly identical primary beam response pattern, we are able to avoid one of the
most debilitating source of error in these measurements: the primary beam.  
% XXX update document map
In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental 
setup, observations and analysis method followed. In \S\ref{sec:fits} we
compare the spectra with available data.  We conclude in 
\S\ref{sec:Conclusion}.

@@

\section{Approach}
\label{sec:approach}
In this section, we describe how we use PAPER in its imaging configuration
to measure Pictor A and a selection of known, bright sources suitable for confirming the accuracy of the measurement
and extrapolated flux scale.

 In \citet{Jacobs:2013p9837} several limitations were identified that
exasperated the primary beam uncertainty.  First, under most imaging schemes, each source flux is measured at just a few 
points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources.
Here we have averaged over long tracks through the primary beam. Using the drift scan-beamforming technique, each 
source is measured hundreds of times at a variety of different pointings. The variation between these measurements is then
used to calculate measurement uncertainty. Second, the flux scale was found to vary substantially over the 
sky, due to the dual uncertainties of primary beam response and prior catalog. As a hedge against beam uncertainty 
we limit our selection to source with similar primary beam responses. A third limitation, identified in \citet{Williams:2012p8768},
was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
uncertainty, we weight the source track by an additional factor of the primary beam model.

\subsection{Selection of confirmation sources}
As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. These paths
provide a detailed sample of the primary beam relative to the peak of the trace, however,
a model is still required to calibrate between declinations and the accuracy of the trace is sometimes contaminated by
sidelobes. In section XXX we will compare the beam response as measured by the PicA trace with the model 
used to estimate flux. We will see that, on average, the primary beam is not the limiting factor in estimating the flux and that
limiting ourselves to a declination range of 10\arcdeg around Pictor A for flux verification is a good compromise.
%
%
%
%This model will be effective over a range of declinations, but will diverge at
%some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
%beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
%stripe width of 5\arcdeg.
%
%\[
%B = dB/dt dt/\theta \Delta \theta
%\]
%
%Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg extrapolation to better
%than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg of the track
%is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg around Pictor A,
%we will have negligible beam area. 
%
%\begin{figure*}
%\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
%\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
%as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
%than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
%for extrapolation over $\sim$5\arcdeg scales.
%  \label{fig:beam_extrapolation}}
%\end{figure*}

@@

The spectra reported here are measured by beam-forming, phasing the visibilities to
the target location, and summing to produce a dynamic spectrum. The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time average is 
weighted by an additional factor of the PAPER's primary beam response 
\citep{pober_et_al2012}.  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M}\\
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S\\ \label{eq:g}
\end{align}

which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
sources at the same declination, and as we found above, diverges slowly from the model in the 10\arcdeg declination stripe.
We estimate this spectral dependent gain for a calibrator (J2331-416) fitting a spectral index model to the
 well-defined data points below 2GHz. This removes an overall offset.

@@

At the output of the beam forming and bandpass calibration step, the flux scale
 is tied to a model fit tp the catalog values of
J2331-416. The accuracy of this fit, and the implied uncertainty in the flux
scale, limits the accuracy of the PAPER measurements..  To refine the flux
scale and estimate our flux scale uncertainty, we bootstrap a single global flux scale 
correction factor using 5
sources selected for their brightness, spectral linearity and data
availability\footnote{Calibration sources:
2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
spectral model we go beyond the data found in Vollmer et al, including all spectral
measurements below 2GHz found in the NED database \footnote{\url{ned.ipac.caltech.edu}: Accessed 1 April 2013}.  These catalog measurements
are primarily by Parkes, and Molonglo with the best precision coming from the
Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
given, we assume uncertainty of 25\%.

@@

\begin{align}
\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
\end{align}

which samples the posterior probability of PAPER data ($SPAPER_{\nu}$) and
catalog values ($Scat_{\nu}$) given a spectral index model for each source and
a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
Marginalizing over the fitted flux scales, we find the resulting flux scale distribution function which is shown in Figure
\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
multiplicative error on every calibrated PAPER measurement.  These errors are added, in quadrature,
to the errors in the PAPER spectra.

These calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  The
resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
at 185MHz. At least half of this error is due to uncertainty in the flux scale.

@@

\begin{equation}
\logL = \sum_\nu{\frac{\left(S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta S_\nu} }
%\label{eq:catlogL}
\end{equation}

@@

\begin{figure}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
\caption{
A more detailed view of the posterior probability distribution. On the left
Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8.
Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.
As above, grey for  the fit to catalog data, black for joint catalog and PAPER
fit.
}
\end{figure}

\section{Results and Discussion}
\label{sec:fits}
In the 59 sources measured, four demonstrated poor convergence fitting a single
spectral index to both the PAPER data and prior catalog data. In three
cases\footnote{1243-412,1247-401,1315-460} %TODO update these sources are in
the Centaurus A/galactic plane region. Though the beam forming method provides
relatively high dynamic range of $\sim$100:1 it is unable to distinguish
between these sources and the bright diffuse Centaurus and galactic structure.
The last source, 0008-421, was not detected by previous PAPER observations and
exhibits flattening at higher frequencies, most likely due to synchrotron
self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains
arrived at a stable posterior distribution. The spectral index parameters for
these chains are given in table \ref{tab:fits}.

Inspecting the confidence contours we find that, for the vast majority ($\sim
75$\%), the PAPER measurements confirm the power law extrapolation from higher
frequencies. The remaining 25\% either A) have large PAPER error bars and
therefore provide no new information or B) do not agree with the spectral index
model.  To understand where most measurements fall on this spectrum we
numerically quantify the overall model improvement derived from the addition of
the PAPER data as 
\begin{align}
\textrm{Improvement} &= \left(\textrm{Precision increase}\right) \left(\textrm{Catalog agreement}\right)\\
&= \left(\frac{1}{Area(\textrm{PAPER})} - \frac{1}{Area(\textrm{Cat})}\right) \left( Area(\PAPER \cap \textrm{Cat}) \right)
\end{align}

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{plots/1526-423_2250-412_2331-416_1932-464_1421-490_gain_mcmc_chain_gain_conf.png}
\caption{
The marginalized PAPER flux scale factor posterior probability distribution
function bootstrapped from the NED database listings for
2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.
\label{fig:gain}}
\end{figure*}

\begin{figure*}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pictor_spectrum.png}
\includegraphics[width=0.49\textwidth]{plots/pic_SI_MCMC.png}
\caption{
Using new PAPER results to constrain the spectrum of Pictor A.  On the left,
the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey
cloud). Inset allows comparison between the 10MHz averaged points with the
403kHz points (grey). The oscillations in the PAPER spectrum are residual side
lobe contamination from other sources and are well represented by the error
bars.  The most reliable prior measurements (dots) are those by
\cite{Wills:1975p9314} at 580MHz and 635MHz \citep{Perley:1997p9312}. The rest
are from with Culgoora \cite{Slee:1995p7541} or Parkes
\cite{Otrupcek:1991p8780} and have been set to the (extrapolated)
\citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC
fits are shown in blue. On the right, the grey contour indicates the 76\%
confidence interval for 150MHz flux and spectral index given the prior data.
Black folds in the PAPER data.
} \label{fig:pic_spectrum}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_3.png}
\caption{
PAPER spectra of 16 sources compared against existing data out of
\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
Figure \ref{fig:pic_spectrum}.\label{fig:srcs3} Sources used to bootstrap the
flux calibration are noted with a *.
}
\end{center}
\end{figure*}

%(PAPER_imaging)danny@keynes:plots$ python sort_SI_plots.py psa64_pic_stripe_perleycorr_SEDfits.txt
%TOP OF MAIN CONFIDENCE PLOT SECTION
%the best sources. High quality fit that improves on previous knowledge
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.9878
\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %1.0085
\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %1.3403
\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.5959
\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.6165
\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %1.0632
\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.1456
\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %3.0727
\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.0991
\includegraphics[width=2in]{plots/0511-484_SI_MCMC.png} %3.3967
\includegraphics[width=2in]{plots/0534-497_SI_MCMC.png} %3.4118
\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1647
\end{center}
\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_1}
\end{figure*}
\clearpage
\begin{figure*}[htbp]2\begin{center}
\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.1506
\includegraphics[width=2in]{plots/0647-475_SI_MCMC.png} %0.8384
\includegraphics[width=2in]{plots/0700-473_SI_MCMC.png} %1.9848
\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.0785
\includegraphics[width=2in]{plots/0748-440_SI_MCMC.png} %0.2942
\includegraphics[width=2in]{plots/0748-454_SI_MCMC.png} %0.0742
\includegraphics[width=2in]{plots/0809-492_SI_MCMC.png} %0.6265
\includegraphics[width=2in]{plots/0819-474_SI_MCMC.png} %0.9749
\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %0.0034
\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0195
\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.0012
\includegraphics[width=2in]{plots/1116-462_SI_MCMC.png} %0.0062
\end{center}
\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_2}
\end{figure*}
\clearpage
\begin{figure*}[htbp]2\begin{center}
\includegraphics[width=2in]{plots/1143-483_SI_MCMC.png} %0.004
\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %0.0163
\includegraphics[width=2in]{plots/1232-416_SI_MCMC.png} %0.0227
\includegraphics[width=2in]{plots/1243-412_SI_MCMC.png} %0.0076
\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %0.06
\includegraphics[width=2in]{plots/1247-401_SI_MCMC.png} %0.1161
\includegraphics[width=2in]{plots/1302-491_SI_MCMC.png} %0.5328
\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.1959

>>>>

\newcommand{\Nconf}{31}
\newcommand{\Nsrc}{32}

@@

\begin{abstract}
We present a catalog of broad-band spectral measurements from the 
Donald C. Backer Precision Array for Probing
the Epoch of Reionization (PAPER) in South Africa observed in July and
September of 2011.  In order to reduce the impact of beam calibration, which proves to
be a difficult endeavor for transit telescopes such as PAPER, on the determination
of source spectra, we have focused on calibrating sources in a narrow declination range.
Since each source follows a nearly identical path through the primary beam, this
restriction allows beam calibration to be greatly reduced as a source of error,
yielding a dramatic improvement in the accuracy of source spectra measured in the 
100--200-MHz band which is receiving renewed attention by experiments seeking to
measure 21cm emission from the Epoch of Reionization (EoR). Using beam forming
and fringe-rate filtering we measure spectra for Pictor A, which provides a key flux reference for PAPER's EoR
power spectrum analysis, 
as well as \Nconf other sources at nearby declinations. Extrapolating from higher frequency
catalogs we set the flux scale in a monte-carlo fit across multiple sources. This fit 
propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
2.4\%.
This accuracy is limited by the uncertainty in the catalog measurements we use
to estimate an absolute flux scale, and represents 
an order of magnitude improvement over previous measurements in this band.  
Comparing with prior measurements, 90\% are found to confirm and refine a power-law model for flux density.

@@

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{furlanetto_et_al2006}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued
foreground characterization is a
vital step en route to any 21-cm EoR detection.
At these low
frequencies the Southern sky is much less well known than the North, 
with catalog source fluxes at 150MHz being inaccurate at the 20\% level
for $\delta<-20$\arcdeg (XXX cite).
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768,Bernardi:2013p9859}.

@@

In this paper, we set out to significantly improve the accuracy of spectral measurements between 
100--200 MHz for a set of bright sources in the declination range -46\arcdeg to -40\arcdeg that
are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
Using the fact that, for this restricted declination range,
sources transit through a nearly identical primary beam response pattern, we are able to avoid one of the
most debilitating source of error in these measurements: the primary beam.  
% XXX update document map
In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental 
setup, observations and analysis method followed. In \S\ref{sec:fits} we
compare the spectra with available data.  We conclude in 
\S\ref{sec:Conclusion}.

@@

\section{Approach}
\label{sec:approach}
In this section, we describe how we use PAPER in its imaging configuration
to measure Pictor A and confirm our results by measuring a  selection of known, bright sources. The fluxes are obtained
by forming beams towards known sources as they drift through the primary beam, calibrating to a single source making a similar track.
These long tracks provide allow us to sidestep primary beam uncertainty to measure accurately calibrated fluxes.

 In \citet{Jacobs:2013p9837} several errors were identified as originating in primary beam uncertainty.
  First, under most imaging schemes, each source flux is measured at just a few 
points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources making
it difficult to decouple flux uncertainty from beam uncertainty.
 Using the drift scan-beamforming technique, each 
source is measured hundreds of times at a variety of different pointings to provide a complete sample of the
flux variance due to primary beam variation.  Second, the flux calibration was found to vary over the 
sky due to the dual uncertainties of primary beam response and prior catalog. To limit our exposure to flux calibration
variation we limit our observations to sources passing within 5\arcdeg of locations which we can directly calibrate
from a single reference source.
 A third limitation, identified in \citet{Williams:2012p8768},
was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
uncertainty, we weight the source track by an additional factor of the primary beam model.

\subsection{Selection of confirmation sources}
As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. These paths
provide a detailed sample of the primary beam relative to the peak of the trace, however,
a model is still required to calibrate between declinations and the accuracy of the trace is sometimes contaminated by
sidelobes. In section XXX we will compare the beam response as measured by the PicA trace with the model 
used to estimate flux. We will see that, on average, the primary beam is not the limiting factor in estimating the flux and that
limiting ourselves to a declination range of 5\arcdeg around calibrator 2331-416 for flux verification is a good compromise.
%
%
%
%This model will be effective over a range of declinations, but will diverge at
%some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
%beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
%stripe width of 5\arcdeg.
%
%\[
%B = dB/dt dt/\theta \Delta \theta
%\]
%
%Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg extrapolation to better
%than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg of the track
%is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg around Pictor A,
%we will have negligible beam area. 
%
%\begin{figure*}
%\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
%\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
%as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
%than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
%for extrapolation over $\sim$5\arcdeg scales.
%  \label{fig:beam_extrapolation}}
%\end{figure*}

@@

\subsection*{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing to produce a dynamic spectrum. The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time average is 
weighted by an additional factor of PAPER's primary beam response 
\citep{pober_et_al2012}.  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
&= g(\delta) S  \label{eq:g}
\end{align}

which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
sources at the same declination.  In simulation we multiplied an early attempt to map the beam \cite{Pober:2012p8800}
by electromagnetic simulations of the PAPER beam and find that it 
diverges slowly with declination, with a maximum of 10\% over 5\arcdeg of declination range.
We estimate this spectral dependent gain at a reference declination of 41\arcdeg36\arcmin using (J2331-416) fitting a spectral index model to the
 well-defined data points below 2GHz.

@@

At the output of the beam forming and bandpass calibration step, the flux scale
 is tied to a model fit of the catalog values of
J2331-416. The accuracy of this fit, and the implied uncertainty in the flux
scale, limits the accuracy of the PAPER measurements..  To refine the flux
scale and estimate our flux scale uncertainty, we bootstrap a single global flux scale 
correction factor using 5
sources selected for their brightness, spectral linearity and data
availability\footnote{Calibration sources:
2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
spectral model we go beyond the data found in Vollmer et al, including all spectral
measurements below 2GHz found in the NED database \footnote{\url{ned.ipac.caltech.edu}: Accessed 1 April 2013}.  These catalog measurements
are primarily by Parkes, and Molonglo with the best precision coming from the
Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
given, we assume uncertainty of 25\%.

@@

\begin{align}
\log\mathcal{L}_s &= \sum_{\nu}\frac{ \left[S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha\right]^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
\frac{ (g S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2} \nonumber \\
\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
\end{align}

which samples the posterior probability of PAPER data ($S_\PAPER^{\nu}$) and
catalog values ($S_\textrm{cat}^{\nu}$) given a spectral index model for each source and
a global flux scale factor ($g$).
Marginalizing over the fitted flux scales, we find the resulting flux scale distribution function which is shown in Figure
\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
J2331-413 calibration, is  $+0.11 ^{+0.05}_{-0.08}$ dB, or a 1.54\%
multiplicative error on every calibrated PAPER measurement.  This flux scale is applied to the PAPER spectra
with the errors added in quadrature.
%gain [dB] 0.03,0.11,0.16

%TODO UPDATE this par
These calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  The
resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
at 185MHz. At least half of this error is due to uncertainty in the flux scale.

@@

\begin{equation}
\logL = \sum_\nu{\frac{\left[S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right]^2}{\Delta S_\nu} }
%\label{eq:catlogL}
\end{equation}

@@

\begin{figure}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
\includegraphics[width=0.49\textwidth]{plots/2323-407_trace_hist.png}
\caption{
A more detailed view of the posterior probability distribution. On the left
Pictor A, on the right 2323-407. Confidence contours range from 0.2 to 0.8. The MCMC
chain reveals the distinctive ``banana'' shape of the posterior
due to correlation between the model parameters.
Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_2}.
Grey plots the fit to catalog data, black for joint catalog and PAPER.
}
\end{figure}

\section{Results and Discussion}
\label{sec:fits}
%TODO Revise all the numbers in this session.
%now we have 32 sources (counting pic)
% 25 have >0 improvement
% 0 have negative
% 6 have 0 overlap
In the 59 sources measured, four demonstrated poor convergence fitting a single
spectral index to both the PAPER data and prior catalog data. In three
cases\footnote{1243-412,1247-401,1315-460} %TODO update these sources are in
the Centaurus A/galactic plane region. Though the beam forming method provides
relatively high dynamic range of $\sim$100:1 it is unable to distinguish
between these sources and the bright diffuse Centaurus and galactic structure.
The last source, 0008-421, was not detected by previous PAPER observations and
exhibits flattening at higher frequencies, most likely due to synchrotron
self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains
arrived at a stable posterior distribution. The spectral index parameters for
these chains are given in table \ref{tab:fits}.

Inspecting the confidence contours we find that, for the vast majority ($\sim
75$\%), the PAPER measurements confirm the power law extrapolation from higher
frequencies. The remaining 25\% either A) have large PAPER error bars and
therefore provide no new information or B) do not agree with the spectral index
model.  To understand where most measurements fall on this spectrum we
numerically quantify the overall model improvement derived from the addition of
the PAPER data as 
\begin{align}
\textrm{Improvement} &= \left(\textrm{Precision increase}\right) \left(\textrm{Catalog agreement}\right)\\
&= \left(\frac{1}{\textrm{Area}(\textrm{PAPER})} - \frac{1}{\textrm{Area}(\textrm{Cat})}\right) \left( \textrm{Area}(\PAPER \cap \textrm{Cat}) \right)
\end{align}
where the area is defined as the number of samples having posterior probability above 76\%.

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_1932-464_0103-453_0547-408_0043-424_gain_mcmc_chain_gain_conf.png}
\caption{
The marginalized PAPER flux scale factor posterior probability distribution
function bootstrapped from the NED database listings for
2250-412,2331-416,1932-464,0103-453,0547-408,0043-424 below 2GHz.
\label{fig:gain}}
\end{figure*}

\begin{figure*}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pictor_spectrum.png}
\includegraphics[width=0.49\textwidth]{plots/pic_SI_MCMC.png}
\caption{
Using new PAPER results to constrain the spectrum of Pictor A.  On the left,
the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey
cloud). Inset allows comparison between the 10MHz averaged points with the
403kHz points (grey). The oscillations in the PAPER spectrum are residual side
lobe contamination from other sources and are well represented by the error
bars.  The most reliable prior measurements (dots) are those by
\cite{Wills:1975p9314} at 580MHz and 635MHz \citep{Perley:1997p9312}. The rest
are from with Culgoora \cite{Slee:1995p7541} or Parkes
\cite{Otrupcek:1991p8780} and have been set to the (extrapolated)
\citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC
fits are shown in grey. On the right, the grey contour indicates the 76\%
confidence interval for 150MHz flux and spectral index given the prior data.
Black folds in the PAPER data.
} \label{fig:pic_spectrum}
\end{figure*}

@@

%(PAPER_imaging)danny@keynes:plots$ python sort_SI_plots.py psa64_pic_stripe_perleycorr_SEDfits.txt
%TOP OF MAIN CONFIDENCE PLOT SECTION
%the best sources. High quality fit that improves on previous knowledge
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.6363
\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %0.7038
\includegraphics[width=2in]{plots/0008-421_SI_MCMC.png} %0.3103
\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %0.8007
\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.3398
\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.6566
\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %0.7536
\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.1772
\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %2.8054
\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.3053
\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1881
\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.3435

\end{center}
\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_1}
\end{figure*}
\clearpage
\begin{figure*}[htbp]2\begin{center}
\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.2743
\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0266
\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.014
\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %0.0514
\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %0.0429
\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.2905
\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.6859
\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0504
\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.3409
\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.2824
\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.2937
\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.2383

\end{center}
\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_2}
\end{figure*}
\clearpage
\begin{figure*}[htbp]2\begin{center}
\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.3487
\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %7.8431
\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.3356
\end{center}
\caption{fits of the next 16 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_3}
\end{figure*}
%BOTTOM OF MAIN CONFIDENCE PLOT SECTION
%%%%%%%%%%%%%%%%%%%%

%BEGIN PASTE

\begin{figure*}[htbp]
\begin{center}
%zero overlap
\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.0

\end{center}
\caption{
These fits are somehow at odds with other measurements.  The 1526-42 spectrum is visibly curved (see Fig. \ref{fig:srcs1), which explains the large disagreement in spectral index but not flux. 1424-418 is an optically polarized quasar with a flat and variable radio spectrum which might imply co-aligned jet viewing and high intrinsic variability. 
} \label{fig:SI_contour_new}
\end{figure*}
